%% Official Elsevier elsarticle template, downloaded from Elsevier's
%% LaTeX instructions page as elsarticle_April2024.
%% AST uses Elsevier submission; numbered references are used per the
%% official numbered elsarticle template. The doubleblind option follows
%% AST's double-anonymized review policy for submission PDFs.
\documentclass[preprint,review,12pt,number,doubleblind]{elsarticle}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage[hypertexnames=false]{hyperref}
\usepackage{url}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{xcolor}
\usepackage{array}
\usepackage{ragged2e}

\journal{Aerospace Science and Technology}

\newcommand{\R}{\mathbb{R}}
\newcommand{\dt}{\Delta t}
\newcommand{\norm}[1]{\left\lVert #1 \right\rVert}
\newcommand{\los}{\mathrm{LOS}}
\newcommand{\fov}{\mathrm{FOV}}
\newcommand{\dv}{\Delta v}
\newcommand{\unit}[2]{#1~#2}
\newcommand{\artifact}[1]{\texttt{\small #1}}

\begin{document}

\begin{frontmatter}

\title{OrbInspect: Coverage-Constrained Relative Trajectory Planning and ROS~2--Gazebo Validation for Autonomous Orbital Structure Inspection}

\author[inst1]{Rugang}
\author[inst2]{OrbInspect Contributors}

\affiliation[inst1]{
  organization={OrbInspect Project},
  city={Shanghai},
  country={China}
}

\affiliation[inst2]{
  organization={Open Research Software Collaboration},
  country={International}
}

\begin{abstract}
Autonomous inspection of large orbital structures requires a planner that can
reason about relative orbital motion, sensor visibility, target coverage,
collision avoidance, and fuel expenditure while remaining reproducible enough
for system-level validation. This paper presents OrbInspect, a ROS~2 Jazzy
simulation and evaluation framework for space-station-scale external inspection.
OrbInspect uses a ROS-native Clohessy--Wiltshire/Hill dynamics node as the
state source of truth, separates quantitative planning from Gazebo Harmonic
visualization, and records trajectory, control, coverage, safety, planner, and
configuration artifacts for paper-grade analysis. We formulate coverage-
constrained inspection as a mixed visibility--dynamics problem and implement a
mesh-aware offline planning experiment with area-weighted target sampling,
line-of-sight filtering, attitude export, and seven planning methods. The best
feasible method, a dynamics-aware weighted set-cover planner followed by a
CW-transfer tour, reached 98.33\% final coverage on 180 mesh targets with 357
candidate viewpoints, 23 selected viewpoints, \unit{8.770}{m/s} cumulative
$\Delta v$, \unit{7.53}{m} minimum clearance, \unit{0.564}{m/s} maximum speed,
and \unit{5.86}{s} planning time. The same benchmark showed that a pure
coverage-greedy baseline also achieved 98.33\% coverage but was infeasible
because its trajectory entered the keep-out envelope, while a random-safe
baseline required \unit{24.57}{m/s}. A ROS~2 execution smoke run produced
synchronized trajectory, control, coverage, planner, safety, and rosbag
artifacts, and Gazebo Harmonic validation using an International Space Station
visual model confirmed replay, pose-following, and visual interface behavior
without making Gazebo physics the authority for spacecraft dynamics.
\end{abstract}

\begin{highlights}
\item OrbInspect separates HCW dynamics authority from Gazebo visualization.
\item A self-contained mesh benchmark reports trajectory, attitude, coverage,
safety, and planner artifacts.
\item The proposed set-cover CW tour reaches 98.33\% mesh-target coverage.
\item The best feasible method reduces $\Delta v$ by 64.3\% relative to the
random-safe baseline.
\item ROS~2 validation records synchronized control, coverage, planner, safety,
and rosbag outputs.
\item Gazebo Harmonic frames and videos validate visual replay, not orbital
physics.
\end{highlights}

\begin{keyword}
spacecraft inspection \sep relative orbital dynamics \sep coverage planning
\sep next-best-view planning \sep Clohessy--Wiltshire equations \sep ROS~2
\sep Gazebo Harmonic \sep reproducible robotics evaluation
\end{keyword}

\end{frontmatter}

\input{sections/01_introduction}
\input{sections/02_related_work}
\input{sections/03_system_and_mission}
\input{sections/04_problem_formulation}
\input{sections/05_algorithm}
\input{sections/06_simulation_protocol}
\input{sections/07_expected_results}
\input{sections/08_limitations}
\input{sections/09_conclusion}

\bibliographystyle{elsarticle-num}
\bibliography{references}

\end{document}
