\section{Introduction}
\label{sec:introduction}

Large orbital structures are becoming central to civil, scientific, and
commercial spaceflight. Space stations, assembled telescopes, logistics
platforms, and in-space manufacturing facilities all require periodic external
inspection to detect configuration changes, micrometeoroid damage, thermal
blanket degradation, docking-interface anomalies, and other faults that are
not easily observed from fixed onboard cameras. The corresponding planning
problem is simultaneously geometric and dynamic. A candidate view may provide
high visual coverage yet remain unsafe, expensive, or unreachable under
relative orbital motion.

Existing inspection planners often emphasize one side of this problem. Robotic
next-best-view methods provide mature tools for coverage, occlusion reasoning,
and sensor placement, but their motion cost is usually geometric. Relative
orbit-design methods provide dynamically meaningful paths, but they do not
always treat surface coverage, camera field of view, and target occlusion as
the planning objective. This separation is limiting for large structures.
Selecting views first and checking dynamics later can produce trajectories
that appear coverage-rich but violate clearance or require excessive input.

The key difficulty is not only that coverage and dynamics must both be
considered, but that the selectable inspection action itself must be physically
meaningful. A static viewpoint is an incomplete planning primitive for orbital
inspection because a view that is geometrically informative may be unreachable,
unsafe during approach, or passively unsafe after thrust loss. Conversely, an
orbit segment that is dynamically natural may be uninformative if its camera
field of view does not expose new target surface. This motivates an inspection
primitive that binds observability and orbital feasibility before planning
begins.

This paper addresses that gap by introducing the safe observable orbital arc
(SOOA). A SOOA is not merely a candidate viewpoint or a transfer edge. It is a
finite-duration inspection action generated under relative orbital dynamics and
annotated with the surface targets observed through the camera model, the
required control effort, the minimum clearance, the input and speed feasibility
status, and a passive-drift safety audit. Planning over SOOAs changes the
finite search space: infeasible or sensor-invalid actions are removed before
coverage selection, rather than repaired afterward. In the present
implementation, geometric viewpoints remain as seeds for transfer-to-dwell
arcs, but the exported and evaluated planning object is the selected SOOA.

The finite graph also gives a precise scope for verification. For a fixed SOOA
library, fixed visibility relation, and fixed feasible-transition graph, the
inspection task can be written as a mixed-integer optimization problem. We
retain an exact dynamic-programming oracle on small exhausted graphs to verify
the discrete SOOA objective. This oracle is not presented as the full-mission
solver; the reported ISS-scale high-coverage trajectories are generated by the
scalable deterministic SOOA planner.

The reported results show that dynamics awareness matters. On the ISS-mesh
benchmark, the proposed SOOA tour achieves 98.33\% coverage with 21
selected inspection actions, \unit{21.592}{m/s} cumulative $\Delta v$, \unit{9.91}{m}
minimum clearance, and \unit{5.97}{s} planning time. Coverage-greedy reaches
the same coverage but requires input beyond the admissible bound and violates
clearance; nearest selection also reaches high coverage but violates
clearance. Safe-coverage and random-safe baselines remain feasible at high
coverage, but require substantially higher cumulative $\Delta v$, while the
fuel-focused baseline stops below the high-coverage target. The comparison
therefore exposes failure modes that are hidden by coverage metrics alone in
this deterministic base case. Robustness across target density, candidate
density, initial state, keep-out margin, and transfer duration is treated as a
separate validation requirement rather than inferred from one mesh instance.

ROS~2 Jazzy and Gazebo Harmonic are used as a replay and verification layer,
not as the source of orbital dynamics. The ROS stack publishes the chaser
state from the HCW dynamics model, records trajectory, attitude, coverage,
safety, and planner logs, and reconstructs the camera frustum used by the
offline planner. Gazebo provides visual context for the station and chaser.
This replay layer verifies that the planned visual geometry can be
instantiated in the integrated system while preserving the planner as the
scientific object of study.

The main contributions are:
\begin{enumerate}
  \item We introduce the safe observable orbital arc (SOOA), an inspection
  motion primitive that jointly encodes HCW relative-motion feasibility,
  FOV-valid surface visibility, line-of-sight coverage, control effort,
  clearance, input feasibility, and passive-safety audit metrics.
  \item We formulate full-coverage orbital inspection as a constrained
  SOOA-selection problem on a finite graph, avoiding the conventional
  separation between geometric viewpoint selection and subsequent dynamic
  feasibility checking.
  \item We develop a scalable deterministic safe-arc coverage solver for
  ISS-scale mesh benchmarks, with an exact dynamic-programming oracle used
  only to verify reduced exhausted SOOA graphs.
  \item We provide a reproducible validation protocol with baseline
  comparisons, sensitivity studies, ablations, and ROS~2/RViz/Gazebo replay
  that verifies trajectory, attitude, camera-frustum, coverage, and safety-log
  consistency while preserving HCW propagation as the quantitative source of
  truth.
\end{enumerate}
