\section{Related Work}
\label{sec:related}

Orbital inspection draws on relative spacecraft motion, robotic view planning,
and orbit-design methods for complex structures. The Clohessy--Wiltshire
equations remain a common starting point for rendezvous and proximity
operations near a circular chief orbit because they provide a linear,
interpretable model of relative translation \cite{clohessy1960terminal}.
Although high-fidelity perturbation models are required for flight design, a
CW/HCW model is appropriate for the planning question studied here: how view
ordering affects fuel use, clearance, and input demand under a fixed relative
dynamics model \cite{wertz2011space}.

Robotic inspection and next-best-view planning study how a robot should select
sensor poses that reconstruct or inspect an object efficiently. Classical
surveys emphasize visibility, occlusion, sensor range, view quality, and the
trade-off between coverage and motion cost \cite{scott2003view}. Kinodynamic
sampling-based planners, including rapidly exploring random trees and their
optimal variants, explicitly combine dynamics and collision constraints during
motion planning \cite{lavalle1998rapidly,karaman2011sampling}. Their strength
is continuous-state reachability, whereas coverage is usually encoded through
task-specific rewards, terminal goals, or repeated replanning rather than as a
finite weighted dwell-coverage objective over a spacecraft surface.

Recent spacecraft-inspection studies illustrate the same tension from
different directions. Apodaca et al. couple viewpoint planning with trajectory
generation for in-orbit structure inspection and emphasize coverage-energy
trade-offs in a supervised planning pipeline \cite{apodaca2025trajectory}.
Hou et al. design relative orbits for visual inspection of the China Space
Station and analyze field-of-view and occlusion feasibility through orbital
geometry \cite{hou2024relative}. Zhou et al. plan tomographic inspection paths
around complex spacecraft structures with surface-aware obstacle avoidance
\cite{zhou2026tomographic}. Ogri et al. address a complementary online
problem: image-based feature tracking, information gain, and dwell-time
conditions for autonomous inspection under switched systems
\cite{ogri2025switched}. The present work is positioned between these lines:
it does not introduce a new orbital dynamics model, a flight-certified
collision-avoidance controller, or a globally optimal continuous planner.
Its contribution is the SOOA abstraction and offline finite-arc solver in
which surface coverage, camera feasibility, HCW transfer effort, clearance,
input saturation, and passive-drift audit metrics are evaluated before an
inspection action can contribute coverage.

The distinction is the planning primitive. Robotic NBV and inspection planners
commonly reason over sensor poses or short geometric motions, while
relative-orbit design methods reason over dynamically meaningful paths that
are not necessarily coverage-optimal. The proposed SOOA representation merges
these two views at the discrete action level: every selectable action is
simultaneously an orbital motion segment and a sensor-valid coverage
contributor. This makes the finite graph a graph of admissible inspection
actions, not merely a graph of geometric views connected by post hoc
transfers.

\begin{table*}[t]
  \centering
  \caption{Positioning relative to closely related inspection and planning
  approaches.}
  \label{tab:positioning}
  \renewcommand{\arraystretch}{1.08}
  \setlength{\tabcolsep}{4.0pt}
  \begin{tabularx}{\textwidth}{@{}>{\RaggedRight\arraybackslash}p{0.18\textwidth}>{\RaggedRight\arraybackslash}p{0.36\textwidth}>{\RaggedRight\arraybackslash}X@{}}
    \toprule
    Approach & Primary emphasis & Difference from this work \\
    \midrule
    Robotic NBV surveys~\cite{scott2003view} &
    geometric surface or volume coverage with sensor-pose sampling &
    motion cost is usually geometric or platform-specific rather than an
    HCW-feasible orbital edge cost \\
    Kinodynamic sampling~\cite{lavalle1998rapidly,karaman2011sampling} &
    continuous-state motion planning with dynamics and collision constraints &
    coverage is typically task-reward driven rather than a finite weighted
    dwell-coverage graph over spacecraft surface targets \\
    Apodaca et al.~\cite{apodaca2025trajectory} &
    inspection coverage and energy trade-off for in-orbit structures &
    does not make the selectable primitive a safety-audited observable orbital
    arc with reduced-graph oracle verification \\
    Hou et al.~\cite{hou2024relative} &
    relative-orbit design for visual inspection with FOV and occlusion checks &
    optimizes orbit geometry rather than selecting finite-duration SOOAs for
    weighted surface coverage \\
    Zhou et al.~\cite{zhou2026tomographic} &
    tomographic inspection paths around complex spacecraft structures &
    targets scan-path planning rather than HCW-feasible dwell-view sequencing
    with input auditing \\
    Ogri et al.~\cite{ogri2025switched} &
    online feature tracking, information gain, and switched-system execution &
    addresses execution-level camera control rather than offline finite-graph
    coverage planning \\
    This work &
    safe observable orbital arcs for FOV-valid weighted surface coverage &
    selects finite-duration HCW-feasible inspection actions annotated with
    visibility, fuel cost, clearance, input feasibility, passive-safety audit,
    reduced-graph oracle verification, and ROS~2/RViz/Gazebo replay \\
    \bottomrule
  \end{tabularx}
\end{table*}

Table~\ref{tab:positioning} clarifies what is gained and lost by the finite
SOOA graph. The gain is a common discrete object on which coverage, camera
feasibility, transition feasibility, clearance, input limits, passive-drift
audit metrics, and reduced-graph oracle checks can be stated simultaneously.
The cost is that optimality is conditional on the sampled SOOA library and
precomputed feasible-transition graph; the approach does not provide global
optimality in continuous viewpoint space, nor does it replace kinodynamic
planning when a mission requires continuous online obstacle avoidance. The
safety statement is therefore planning-level feasibility filtering and audit
on logged HCW rollouts, not a flight safety certificate.

Simulation frameworks for space robotics must also be treated carefully. A
rendered Gazebo scene can provide visual context and reveal integration errors
in camera geometry, but standard rigid-body physics in a robotics simulator is
not a substitute for orbital relative dynamics. We therefore use Gazebo
Harmonic for station and chaser visualization while the ROS~2 dynamics node
publishes the state used by replay, safety checks, camera-frustum
verification, and logging. This separation makes the validation repeatable
without allowing simulator physics to define the scientific result.
