\section{System Model and Mission Setting}
\label{sec:system}

The mission is divided into an offline planning problem and an execution
verification problem. Offline planning receives the station geometry, initial
relative state, camera parameters, keep-out distance, and actuation limits. It
returns a time-indexed reference trajectory, a camera-attitude stream, and
summary metrics for coverage, effort, clearance, and feasibility. Execution
then replays or tracks this reference and checks that the logged state,
attitude, and camera frustum are consistent with the planning model. The
planner is therefore evaluated by HCW-based trajectory and camera outputs,
whereas ROS~2 and Gazebo verify integration and visual geometry.

\subsection{Reference Frame and Dynamics}

The inspection pass is represented in a local-vertical/local-horizontal frame
attached to a nominal circular chief orbit. Over the time horizon considered
here, the inspected structure is treated as fixed in this frame. The chaser
translational state is
\begin{equation}
  x =
  \begin{bmatrix}
    r_x & r_y & r_z & v_x & v_y & v_z
  \end{bmatrix}^{\mathsf{T}},
\end{equation}
where $r \in \R^3$ is relative position and $v \in \R^3$ is relative velocity.
The camera boresight is modeled through an attitude variable or an equivalent
unit pointing vector. In the baseline mission, attitude enters the visibility
predicate and the replay stream, while closed-loop attitude dynamics are left
outside the offline optimization. This scope isolates the coupling between
surface coverage and translational orbital motion.

The baseline dynamics are the Clohessy--Wiltshire equations,
\begin{align}
  \dot r &= v, \\
  \dot v &=
  \begin{bmatrix}
    3n^2 r_x + 2n v_y + a_x \\
    -2n v_x + a_y \\
    -n^2 r_z + a_z
  \end{bmatrix},
\end{align}
where $n$ is the chief mean motion and
$u=[a_x,a_y,a_z]^{\mathsf{T}}$ is the commanded acceleration. The discrete
propagation map is
\begin{equation}
  x_{k+1}=f_{\mathrm{CW}}(x_k,u_k,\dt).
\end{equation}
The same model is used in the offline trajectory generator and in the ROS
dynamics node. Gazebo is not used to propagate the spacecraft state in the
reported experiments.

\subsection{Inspection Geometry and Termination}

The inspected structure is represented for planning by a finite set
$\mathcal{T}=\{1,\ldots,N\}$ of target samples. Each target $i$ has a point
$p_i$, outward normal $n_i$, and nonnegative weight $w_i$ proportional to the
surface area represented by that sample. A target is considered inspected when
it has remained visible for at least $\tau_{\min}$. The baseline formulation
does not include solar illumination dynamics; if required by a mission
scenario, illumination can be added as a binary feasibility predicate. The
primary offline benchmark uses the public NASA Solar System ISS glTF model as
the station geometry source~\cite{nasa_iss_gltf_model}, with 180
area-weighted target samples and 357 viewpoint seeds used to generate SOOAs. The mesh defines
target samples, visibility tests, and replay geometry; it is not a dynamics
model.

The mission starts from a safe initial relative state and terminates when a
coverage threshold is reached, when the planner exhausts available useful
inspection actions, or when a maximum mission time is reached. For a weighted target
set, the final coverage ratio is
\begin{equation}
  C_K = \frac{\sum_{i=1}^{N} w_i y_{i,K}}{\sum_{i=1}^{N} w_i},
  \qquad
  y_{i,K}=\mathbf{1}\{\tau_{i,K}\ge \tau_{\min}\}.
\end{equation}
The high-coverage offline benchmark uses a 70\% success threshold and a 98\%
planning stop ratio. These two values have different roles: the former defines
mission success, whereas the latter asks the planner to continue collecting
coverage after success so that high-coverage behavior can be compared across
baselines. The best feasible method reached 98.33\% final coverage, as
reported in Section~\ref{sec:results}.
