\section{Problem Formulation}
\label{sec:problem}

\subsection{State, Visibility, and Coverage}

Let the chaser state at discrete time $k$ be
\begin{equation}
  x_k =
  \begin{bmatrix}
    r_k^{\mathsf T} & v_k^{\mathsf T}
  \end{bmatrix}^{\mathsf T} \in \R^6,
\end{equation}
where $r_k \in \R^3$ and $v_k \in \R^3$ are the relative position and velocity
in the local-vertical/local-horizontal frame of a nominal circular chief orbit.
The inspected structure is represented by a finite weighted target set
\begin{equation}
  \mathcal T = \{(p_i,n_i,w_i)\}_{i=1}^{N},
\end{equation}
where $p_i \in \R^3$ is the target point, $n_i$ is the outward surface normal,
and $w_i \ge 0$ is the inspection weight of that sample.

The camera attitude is represented by a unit boresight vector $b(q_k)\in\mathbb
S^2$ or, equivalently, by an attitude variable $q_k$ that determines the
boresight. Illumination is not modeled as a state variable in the baseline
formulation; it can be included as an additional binary feasibility predicate
when mission lighting constraints are relevant.

Target $i$ is visible at time $k$ if range, field-of-view, incidence angle, and
line-of-sight constraints all hold:
\begin{align}
  \rho_{\min} \le \norm{p_i-r_k} \le \rho_{\max}, \label{eq:range}\\
  \arccos\!\left(\frac{(p_i-r_k)^{\mathsf T} b(q_k)}{\norm{p_i-r_k}}\right)
  \le \alpha_{\max}, \label{eq:fov}\\
  \arccos\!\left(\frac{(r_k-p_i)^{\mathsf T}n_i}{\norm{r_k-p_i}\norm{n_i}}\right)
  \le \theta_{\max}, \label{eq:view-angle}\\
  \los(r_k,p_i,\mathcal O) = 1, \label{eq:los}
\end{align}
where $\alpha_{\max}$ is the half-angle field-of-view limit, $\theta_{\max}$
is the maximum incidence angle, and $\mathcal O$ denotes the occluding
geometry. The dwell state evolves as
\begin{equation}
  \tau_{i,k+1} =
  \begin{cases}
    \tau_{i,k}+\dt, & \text{if target } i \text{ is visible at } k,\\
    \tau_{i,k}, & \text{otherwise}.
  \end{cases}
\end{equation}
The inspection indicator is $y_{i,k}=\mathbf 1\{\tau_{i,k}\ge \tau_{\min}\}$.

\subsection{Dynamic Feasibility and Cost}

The relative translational motion follows the discrete HCW model
\begin{equation}
  x_{k+1}=f_{\mathrm{HCW}}(x_k,u_k,\dt),
\end{equation}
where $u_k\in\R^3$ is the commanded acceleration. The chaser must satisfy the
actuation and safety limits
\begin{align}
  \norm{u_k}_2 &\le u_{\max}, \\
  \norm{v_k}_2 &\le v_{\max}, \\
  d_{\mathcal S}(r_k) &\ge d_{\mathrm{safe}},
\end{align}
where $d_{\mathcal S}(r_k)$ is the signed distance to the station safety
envelope. A CBF-type filter can be attached later as an execution layer, but
it is not part of the core mathematical problem.

The offline planner evaluates motion between SOOA terminal poses through
bounded HCW rollouts. For a transition from arc $a_a$ to arc $a_b$, let
$\pi_{ab}$ denote the sampled state-control sequence generated over a fixed or
bounded transfer duration. The terminal state is constrained to reach the seed
dwell position with zero relative velocity, so each selected SOOA corresponds
to a stabilized inspection action rather than a fly-through point.
The transfer is feasible when every sample satisfies the input, speed, and
clearance constraints and the terminal position and velocity errors remain
within prescribed tolerances. We write this feasibility indicator as
\begin{equation}
  \eta_{ab} =
  \mathbf{1}\{\pi_{ab}\ \text{satisfies all dynamic and safety limits}\}.
\end{equation}
The corresponding edge cost is
\begin{equation}
  \begin{aligned}
  \ell_{ab} ={}&
  \lambda_v \sum_{k\in\pi_{ab}}\norm{u_k}_2\dt
  + \lambda_t T_{ab} \\
  &+ \lambda_s \sum_{k\in\pi_{ab}}\phi(d_{\mathcal S}(r_k))
  + \lambda_e e_{ab},
  \end{aligned}
\end{equation}
where $T_{ab}$ is transfer duration, $e_{ab}$ is terminal tracking error,
including terminal position and velocity residuals, and $\phi$ penalizes
proximity to the safety boundary. Edges with $\eta_{ab}=0$
are either removed from the reduced finite graph or assigned a prohibitive cost
in greedy baselines.
The coverage mission ends when either the prescribed stop ratio is
reached, the finite view budget is exhausted, or no feasible outgoing edge
remains from the current terminal state.

\subsection{Safe Observable Orbital Arc}

A safe observable orbital arc is the finite-duration inspection action used by
the planner. For an arc $a_j$ over $t\in[0,T_j]$, define
\begin{equation}
    a_j = \left(x_j(t), u_j(t), q_j(t), \Gamma_j,
    \Delta v_j, d^{\min}_j, \rho_j\right),
\end{equation}
where $x_j(t)$ is the HCW-propagated relative state, $u_j(t)$ is the commanded
acceleration, $q_j(t)$ is the camera attitude profile, $\Gamma_j\subseteq
\mathcal{T}$ is the set of targets satisfying the range, FOV, incidence,
dwell, and line-of-sight visibility predicates for the stabilized inspection
action, $\Delta v_j$ is the accumulated control effort, $d^{\min}_j$ is the
minimum clearance, and $\rho_j$ is the passive-safety audit margin.

The accumulated control effort and clearance are
\begin{equation}
    \Delta v_j = \int_0^{T_j} \|u_j(t)\|_2\,dt,
\end{equation}
\begin{equation}
    d^{\min}_j = \min_{t\in[0,T_j]} d_{\mathcal{S}}(r_j(t)).
\end{equation}
An arc is dynamically admissible if all sampled states satisfy the HCW
propagation model, input bound, speed bound, clearance bound, and terminal
error tolerance. It is observable if $\Gamma_j\neq\emptyset$ under the camera
visibility model.

To audit passive safety, the uncontrolled drift from sampled states on the arc
is propagated as
\begin{equation}
    \dot{x}_{\mathrm{drift}} = f_{\mathrm{HCW}}(x_{\mathrm{drift}},0).
\end{equation}
The reported passive-safety margin is
\begin{equation}
    \rho_j = \min_{t_k\in a_j}\min_{\tau\in[0,T_{\mathrm{PS}}]}
    d_{\mathcal{S}}\left(r^{\mathrm{drift}}(t_k+\tau)\right)-d_{\mathrm{PS}}.
\end{equation}
The arc is passively safe when $\rho_j\ge 0$. This is a planning-level audit
under the sampled HCW model and the selected audit horizon; it is not a
flight-certified safety guarantee.

\subsection{Optimization Objective}

The offline inspection problem is to choose a sequence of viewpoints and
controls that maximizes weighted coverage while remaining dynamically feasible:
\begin{equation}
  \begin{aligned}
  \min_{\mathcal X,\mathcal U,\mathcal Q}\quad & J_{\mathrm{total}} \\
  ={}& w_C (1-C_K) + w_T K\dt \\
  &+ w_U \sum_{k=0}^{K-1}\norm{u_k}_2\dt \\
  &+ w_S \sum_{k=0}^{K}\phi\!\left(d_{\mathcal S}(r_k)\right) \\
  &+ w_A \sum_{k=0}^{K}\psi(q_k) \\
  \mathrm{s.t.} \quad
  & x_{k+1}=f_{\mathrm{HCW}}(x_k,u_k,\dt), \\
  & \norm{u_k}_2 \le u_{\max}, \quad \norm{v_k}_2 \le v_{\max}, \\
  & d_{\mathcal S}(r_k)\ge d_{\mathrm{safe}}, \\
  & y_{i,k} \text{ follows the visibility and dwell model}, \\
  & C_K \ge C_{\mathrm{req}}.
  \end{aligned}
\end{equation}
Here $\mathcal X=\{x_k\}_{k=0}^{K}$, $\mathcal U=\{u_k\}_{k=0}^{K-1}$,
and $\mathcal Q=\{q_k\}_{k=0}^{K}$. The function $\phi(\cdot)$ penalizes
proximity to the safety boundary and $\psi(q_k)$ penalizes attitude or
boresight deviation if attitude is optimized explicitly.
The weighted coverage ratio is
\begin{equation}
  C_K = \frac{\sum_{i=1}^{N} w_i y_{i,K}}{\sum_{i=1}^{N} w_i}.
\end{equation}

\subsection{Finite Graph and Evaluation Quantities}

This is a mixed-integer, nonconvex planning problem. The discrete components
are target visibility, dwell satisfaction, and SOOA selection. The
continuous components are HCW propagation, actuation limits, and clearance
constraints. The present benchmark studies the finite approximation induced
by a SOOA graph. Seed viewpoints generate terminal/dwell camera poses, but the
accepted graph elements are finite-duration HCW-feasible inspection arcs.

Let $\mathcal A=\{a_j\}_{j=1}^{M}$ be the accepted SOOA library and let
$\Gamma(a_j)\subseteq\mathcal T$ be the target subset visible from arc $a_j$.
For a maximum of $L$ selected arcs, the finite planning problem is to choose an
ordered sequence
\begin{equation}
  \sigma=(a_{\sigma_1},\ldots,a_{\sigma_L})
\end{equation}
that satisfies feasible-transfer constraints and covers enough target weight.
One representative objective is
\begin{equation}
  \begin{aligned}
  J_{\mathrm{graph}}(\sigma)={}&
  \sum_{\ell=1}^{L}\ell(a_{\sigma_{\ell-1}},a_{\sigma_\ell})
  + \lambda_v\sum_{\ell=1}^{L}\Delta v(a_{\sigma_\ell})\\
  &+\lambda_L L
  +\lambda_C\sum_{i=1}^{N}w_i(1-c_i).
  \end{aligned}
\end{equation}
where $a_{\sigma_0}$ denotes the initial state action and
\begin{equation}
  c_i = \mathbf{1}\left[
  i\in \bigcup_{\ell=1}^{L}\Gamma(a_{\sigma_\ell})\right].
\end{equation}
The coverage
constraint is
\begin{equation}
  \sum_{i=1}^{N}w_i c_i
  \ge C_{\mathrm{req}}\sum_{i=1}^{N}w_i .
\end{equation}
This finite graph is the object on which the exact optimality statement in
Section~\ref{sec:theory} is made. The implementation evaluated in
Section~\ref{sec:results} uses a scalable deterministic safe-arc coverage
solver on the same graph.

For reporting, the primary quantities are cumulative control effort, minimum
clearance, peak requested input, mission time, and selected-SOOA count:
\begin{align}
  \Delta v_{\mathrm{cum}} &= \sum_k \norm{u_k}_2\dt,\\
  d_{\min} &= \min_k d_{\mathcal S}(r_k),\\
  u_{\max,\mathrm{req}} &= \max_k \norm{u_k}_{\mathrm{req},2}.
\end{align}
These quantities are used later to compare planners on the same mission
geometry and relative dynamics model.
