\section{Offline Planner}
\label{sec:algorithm}

\subsection{Decomposition}

The offline solver operates on the finite graph defined in
Section~\ref{sec:problem}. It decomposes inspection into target sampling,
candidate-view construction, visibility-matrix construction, HCW edge
generation, finite-graph optimization, trajectory rollout, and camera-attitude
export. The implementation has two modes. The certified mode solves a reduced
finite graph exactly by dynamic programming over selected-view masks and the
last visited view. The scalable mode uses dynamics-aware set cover followed by
CW-cost tour ordering for the full ISS-mesh benchmark. Both modes use the same
camera visibility matrix and the same HCW transfer feasibility audit, so the
certificate and the scalable results refer to the same discretized mission
model.

\subsection{Candidate Viewpoints}

For each surface target, candidate views are generated on offset shells and
accepted only when they satisfy basic range, field-of-view, incidence-angle,
line-of-sight, and clearance constraints. Each candidate $z_j$ stores a safety
margin and a precomputed set of visible targets. The resulting binary
visibility relation can be written as
\begin{equation}
  A_{ij}=1
  \quad \Longleftrightarrow \quad
  \text{target } i \text{ is visible from candidate } z_j .
\end{equation}
In the high-coverage offline benchmark, 357 candidates are generated for
180 mesh target samples.

\subsection{Dynamics-Aware Viewpoint Selection}

The scalable solver selects views on the candidate graph and then orders the
selected sequence using CW transfer costs. At each selection step, the planner
balances new weighted coverage against the HCW transfer cost from the current
predicted state. For candidate $z_j$, let $\Delta C_j$ be the newly gained
weighted coverage and let $J(x,z_j)$ be the rollout cost defined by the edge
model in Section~\ref{sec:problem}. The selection stage uses the score
\begin{equation}
  s_j =
  \frac{\Delta C_j}{1+J(x,z_j)}
  + w_m \min\{\widehat{d}_{\min}(x,z_j),d_{\max}\},
\end{equation}
then updates the predicted state with the CW rollout to the selected viewpoint.
The resulting ordered sequence is then propagated forward so that later choices
depend on the orbital state reached by earlier ones. The planner records the
selected candidate identifier, new target count, area gain, cumulative
coverage, score, transfer $\Delta v$, dynamic transfer cost, minimum
clearance, transfer tracking error, and feasibility flag for each selected
viewpoint.
The planning loop terminates when the cumulative coverage reaches the
prescribed stop ratio, when the view budget is exhausted, or when no feasible
outgoing edge remains from the current state.

\subsection{CW Transfer Generation}

After a candidate is selected, the planner computes a finite-horizon HCW
terminal transfer to the selected viewpoint. For the fixed integration grid,
the linear HCW map is used to solve the minimum-energy sequence of piecewise
constant accelerations whose terminal position equals the candidate view
position and whose terminal relative velocity is zero. The transfer is then
sampled forward, and the edge is marked feasible only when terminal position
error, terminal speed, peak input, speed, and clearance satisfy the specified
bounds. This makes the selected viewpoints stabilized inspection states rather
than fly-through camera markers.
Because each segment is generated independently on the discrete HCW grid, the
reported trajectory is physically valid but piecewise smooth rather than a
single globally optimized spline. The plotted line is a stitched sequence of
rest-to-rest transfers, so corners can appear at viewpoint transitions even
though each segment satisfies the HCW dynamics model.

The exported trajectory includes position, velocity, acceleration command,
camera boresight, yaw, pitch, and quaternion samples, so the planned path
specifies both where the chaser flies and how the inspection camera is
pointed. Edges that violate feasibility checks are penalized or rejected
depending on the baseline method. Thus, the same visibility gain can be
accepted or rejected depending on whether the terminal HCW transfer remains
inside the control and clearance envelope. The high-coverage benchmark
evaluates the scalable graph solver rather than claiming a global
mixed-integer optimum for the continuous mission.

\input{algorithms/offline_planner}

\subsection{Certified Finite-Graph Solver}
\label{sec:theory}

Let $\mathcal V=\{z_j\}_{j=1}^{M}$ denote the finite candidate-viewpoint set.
Each viewpoint $z_j$ observes a subset of targets $\Gamma_j \subseteq \mathcal
T$, and each directed transfer $(z_a,z_b)$ has a precomputed HCW cost
$\ell_{ab}\ge 0$ and feasibility flag $\eta_{ab}\in\{0,1\}$. The discretized
mission is therefore a finite optimization problem on
$\mathcal G=(\mathcal V,\mathcal E)$, where $\mathcal E$ contains only
feasible transfers.

Let $\Sigma_{L_{\max}}$ be the set of all ordered candidate sequences of
length at most $L_{\max}$ that start from the initial node $z_0$ and use only
feasible edges. For
$\sigma=(z_{\sigma_1},\ldots,z_{\sigma_L})$, define
\begin{align}
  c_i(\sigma) &=
  \mathbf{1}\{i\in\cup_{\ell=1}^{L}\Gamma_{\sigma_\ell}\},\\
  J_{\mathrm{disc}}(\sigma) &=
  \sum_{\ell=1}^{L}\ell_{\sigma_{\ell-1},\sigma_\ell}.
  \label{eq:finite-mip-objective}
\end{align}
The exact finite inspection problem is
\begin{equation}
  \begin{aligned}
  \sigma^\star=\arg\min_{\sigma\in\Sigma_{L_{\max}}}\quad
  & J_{\mathrm{disc}}(\sigma)\\
  \mathrm{s.t.}\quad
  & \sum_{i=1}^{N}w_i c_i(\sigma)
  \ge C_{\mathrm{req}}\sum_{i=1}^{N}w_i .
  \end{aligned}
\end{equation}
This sequence problem can be encoded as a mixed-integer program with
stage-selection and edge-consistency variables. In the implementation, the
certified mode solves it directly by dynamic programming. A state is
$(B,j)$, where $B\subseteq\mathcal V$ is the selected-view set and $j$ is the
last selected view. The value $D(B,j)$ stores the minimum HCW dynamic cost of
any feasible sequence that visits exactly $B$ and terminates at $j$. The
recursion is
\begin{equation}
  D(B\cup\{k\},k)=
  \min_{j\in B,\ \eta_{jk}=1}
  \left[D(B,j)+\ell_{jk}\right],
\end{equation}
with initialization from the initial spacecraft state. The solver returns the
lowest-cost state whose accumulated weighted coverage satisfies the required
ratio before the view budget is exceeded. If all reachable states within the
budget are expanded before the time and expansion limits are reached, the
returned sequence is certified optimal on the reduced graph.

\begin{theorem}[Global optimality on the discretized mission graph]
For a fixed finite candidate set $\mathcal V$, fixed visibility sets
$\Gamma_j$, fixed edge costs $\ell_{ab}$, fixed feasibility indicators
$\eta_{ab}$, required weighted coverage $C_{\mathrm{req}}$, and finite horizon
$L_{\max}$, the dynamic-programming solver described above returns a minimum
cost feasible inspection sequence for the discretized mission graph whenever
it terminates after expanding all reachable states within the horizon.
\end{theorem}

\begin{IEEEproof}[Sketch]
The sequence set $\Sigma_{L_{\max}}$ is finite because both the candidate set
and maximum sequence length are finite. Removing dynamically infeasible edges
only reduces this set. The objective assigns a finite scalar value to every
feasible sequence, and the coverage constraint selects a finite subset of
those sequences. If that subset is nonempty, a minimum is attained. The dynamic
program stores the minimum cost for every reachable pair $(B,j)$ by Bellman's
principle of optimality: any optimal sequence ending at $j$ through selected
set $B$ must contain an optimal predecessor sequence ending at some
$a\in B\setminus\{j\}$. Exhausting all reachable states of cardinality
$\le L_{\max}$ therefore evaluates every feasible ordered sequence up to
duplicate prefixes represented by the same state. Taking the least-cost state
that satisfies the weighted coverage constraint gives the global optimum on
the discretized graph.
\end{IEEEproof}

The theorem is deliberately discrete. It does not claim global optimality for
the original continuous viewpoint space, nor does it claim that the scalable
solver used in the full ISS benchmark is globally optimal. Rather, it
identifies the finite problem for which a certificate is meaningful. In the
reported certification smoke case, the exact solver uses 8 candidate nodes and
13 visible target IDs, expands 39 feasible states, selects two views, reaches
the required 25\% coverage, and returns certificate status ``optimal''. The
same candidate graph can therefore support a fast solver for large studies and
an exact solver for smaller certification cases.

\subsection{Planner Outputs}

The planner outputs a timestamped reference trajectory
\begin{equation}
  \mathcal{P} =
  \{(t_k,r_k^{\mathrm{ref}},v_k^{\mathrm{ref}},u_k^{\mathrm{ref}})\}_{k=0}^{K}.
\end{equation}
For the reported proposed tour, $\mathcal{P}$ contains 945 trajectory samples
over 1890~s with a 90~s transfer duration and 2~s integration step. The
corresponding attitude stream also contains 945 samples. The trajectory and
attitude stream are subsequently available to the ROS stack for replay,
logging, RViz inspection, and Gazebo visualization. In the paper, these outputs
are algorithmic outputs; ROS and Gazebo form the verification environment.
