\section{Execution and Experimental Protocol}
\label{sec:simulation}
\label{sec:online}

The experiments are organized around the offline planner. The ROS~2 and
Gazebo layers are used after planning to replay the saved trajectory,
instantiate the camera geometry, and check integration consistency. They are
not used as the source of orbital dynamics or as an additional optimizer.

\subsection{Benchmark Definition}

The experiments separate certification from scalability. The certification
case uses a reduced ISS-mesh instance with 24 sampled surface targets, 16
generated viewpoint seeds, and an exact solver limit of eight reduced SOOA
nodes. The exact dynamic program minimizes HCW dynamic cost subject to feasible
transitions, a four-arc budget, and a 25\% coverage requirement. This case is
small enough to exhaust the reachable finite graph and therefore tests the
reduced-graph oracle implemented in Algorithm~\ref{alg:certified-dp}.

The primary full-scale quantitative benchmark uses the open NASA ISS glTF mesh
geometry~\cite{nasa_iss_gltf_model}, CW/HCW dynamics, 180 area-weighted mesh
targets, 357 viewpoint seeds, a 70\% coverage success threshold, and a
98\% planning stop ratio. This benchmark uses the scalable SOOA/CW tour solver
rather than the exact dynamic program. It compares the
proposed tour with coverage-greedy, safe coverage-greedy, nearest-viewpoint,
fuel-focused, CW-NBV, and random-safe baselines. All methods use the same
SOOA seed set, visibility model, transfer duration, input limit, keep-out
distance, and termination logic. A run terminates when the stop ratio is
reached, when the SOOA budget is exhausted, or when no feasible outgoing
transfer remains. Older Monte Carlo outputs are retained only as software
regression checks; the manuscript's quantitative claims are based on the
certification case, the deterministic high-coverage mesh comparison, and the
validation matrix below.

To test whether the base-case conclusion is an artifact of one discretization,
we also run the sensitivity and ablation matrix in
Table~\ref{tab:validation-matrix}. The matrix is generated by the same
experiment runner and writes the same CSV/JSON schema as the base benchmark:
per-method coverage, cumulative $\Delta v$, peak requested input,
clipped-step ratio, minimum clearance, selected-SOOA count, mission duration,
and planning time.

\begin{table}[t]
  \centering
  \caption{Validation matrix for sensitivity and ablation studies.}
  \label{tab:validation-matrix}
  \renewcommand{\arraystretch}{1.05}
  \setlength{\tabcolsep}{4.0pt}
  \begin{tabularx}{\linewidth}{@{}>{\RaggedRight\arraybackslash}p{0.34\linewidth}>{\RaggedRight\arraybackslash}X@{}}
    \toprule
    Study & Sweep \\
    \midrule
    Target density & $N=180,500$ comparison; $N=1000$ proposed-only stress case \\
    Candidate density & candidate stride $\in\{1,2,3\}$ \\
    Initial condition & three safe initial relative states \\
    Safety and duration & keep-out distance $\in\{1,2,4\}$~m; segment duration
    $\in\{70,90,120\}$~s \\
    Ablation & remove transfer cost, clearance filtering, input checking, or
    coverage weighting \\
    \bottomrule
  \end{tabularx}
\end{table}

\subsection{Online Replay Interface}

The offline planner exports
\begin{equation}
  \mathcal{P}=\{(t_k,r_k^{\mathrm{ref}},v_k^{\mathrm{ref}},u_k^{\mathrm{ref}},
  q_k^{\mathrm{ref}})\}_{k=0}^{K},
\end{equation}
where $q_k^{\mathrm{ref}}$ defines the camera attitude. Online execution
tracks this sequence using the current state estimate $\hat{x}_k$ and a
nominal law
\begin{equation}
  u_k^{\mathrm{nom}} = u_k^{\mathrm{ref}} + K_x(\hat{x}_k - x_k^{\mathrm{ref}}),
\end{equation}
with $K_x$ chosen for the HCW linearization. A runtime safety layer can pass
the nominal command through the quadratic-program CBF filter
\begin{align}
  u_k^{\mathrm{exec}} = \arg\min_{u \in \R^3}\quad & \norm{u-u_k^{\mathrm{nom}}}_2^2 \\
  \mathrm{s.t.}\quad &
  h(x_k) \ge 0, \nonumber\\
  & \dot{h}(x_k,u) + \alpha h(x_k) \ge 0, \nonumber\\
  & \norm{u}_2 \le u_{\max}, \nonumber
\end{align}
where $h(x_k)=d_{\mathcal S}(r_k)-d_{\mathrm{safe}}$ and $\alpha>0$ is a
barrier gain. A new offline plan is requested if the tracking error exceeds a
tolerance, the barrier filter remains active beyond a prescribed duration, the
executed coverage falls behind its predicted envelope, or the state estimator
reports loss of consistency. This layer defines the execution interface; the
planner itself remains offline.

\subsection{ROS/Gazebo Verification}

The ROS execution run records odometry, nominal control, safe control,
coverage map, mission events, safety status, planner events, camera attitude,
and field-of-view topics. The replay node reconstructs the camera frame from
the saved attitude stream, publishes the boresight marker, and generates the
camera frustum from the same field-of-view parameters used during planning.
This verifies that the visual model used in the offline visibility predicate
can be instantiated consistently at runtime.

Gazebo Harmonic is used to visualize the station and chaser after the ROS
state and camera streams have been reconstructed. The validation artifacts
include preview frames and videos from chaser-follow and whole-structure views
with a camera-frustum overlay. Gazebo does not determine the spacecraft state
in these experiments. The chaser pose is driven from the ROS state stream, so
the dynamics node remains the source of truth.
