\section{Conclusion}
\label{sec:conclusion}

This paper formulated autonomous inspection of orbital structures as a
dynamics-aware coverage-planning problem on a finite candidate-view graph. The
planner incorporates CW/HCW transfer cost, clearance, and input limits during
view selection instead of checking them after geometric coverage has been
chosen. The reduced-graph certification case showed that the implemented
dynamic program can return a true finite-graph optimum: with eight candidate
nodes and 13 visible target IDs, it expanded 39 feasible states and selected a
minimum-cost two-view tour satisfying the 25\% coverage requirement. On the
full ISS-mesh benchmark, the scalable solver generated a feasible 1890~s
trajectory with 21 selected views, 21.5921~m/s cumulative $\Delta v$,
9.9107~m minimum clearance, and 98.33\% final coverage over 180 surface
targets. Compared with coverage-greedy, safe-coverage, nearest-viewpoint,
fuel-focused, CW-NBV, and random-safe baselines, the proposed solver reached
the target coverage with the lowest cumulative $\Delta v$ among feasible
high-coverage methods and avoided the input and clearance violations observed
in simpler high-coverage selection rules. ROS~2 and Gazebo provided replay and
camera-geometry verification, while the planner and logged HCW trajectory
remained the basis of the quantitative claims.

Additional sensitivity and ablation runs show that the proposed planner
remains feasible for the tested $N=500$ target-density case, three initial
states, three candidate densities, and keep-out margins from 1 to 4~m. They
also expose real limits: a 70~s transfer segment violates the input bound, and
a coarse $N=1000$ stress case falls below the high-coverage stop target.
Future work should therefore focus on accelerated mesh visibility, denser
candidate generation, broader Monte Carlo cases, larger certified graph
instances, and uncertainty-aware keep-out, camera slew, illumination, and
actuator constraints. Higher-fidelity validation, including an optional
Basilisk backend, should be added only after the HCW baseline remains
reproducible.
